Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
fromat testing results

\paragraph{The Levels}

@@

\paragraph{The Behaviors}

@@

\paragraph{Combining four objects}\label{document:combining_four_objects}

When combining four objects into one, some comparisons are executed to ensure that the resulting piece is a valid  combination.
\begin{itemize}
  \item The right side of the object in the top left position is compared with the left side of the object in the top right position~\cref{fig:merge_pieces}(1).
  \item The bottom side of the objection the top right position is compared with the top side of the object in the bottom right position~\cref{fig:merge_pieces}(2).
  \item The left side of the objection the bottom right position is compared with the right side of the object in the bottom left position~\cref{fig:merge_pieces}(3).
  \item The top side of the objection the bottom left position is compared with the bottom side of the object in the top left position~\cref{fig:merge_pieces}(4).
\end{itemize}

@@

@@

\section{Testing Results}

In this section, the solver proposed by this paper will be put to the test.
This evaluation serves two key purposes:

\begin{itemize}
  \item Gaining insight into the performance and limitations of the proposed algorithm.
  \item Conducting tests using both digital and real-world jigsaw puzzles to discern the distinctions between the two contexts.
\end{itemize}

\subsection{Setup}
See~\cref{document:dataset} for a detailed
description of the setup.

\begin{figure}[H]
  \caption{Effect of jitter on jigsaw pieces}\label{fig:jiiter}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/jitter.png}
\end{figure}

The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in section
\cref{document:combining_four_objects} were set at different values
depending on the nature of the puzzle (real or digital).

\subsubitem{Effect of Jitter on Execution Time}

Intuitively increasing the jitter would make the pieces harder to
match with each other, and consequently making the puzzle easier to solve.
And we can observe that this intuition is correct in the table below.

This shows how the execution time can be six times faster just by making
each piece more unique. This notion can be applied to the real world puzzle,
in fact the current version of the comparator REF is not using the color
of the piece, only the shape. Adding the color to the available
data could significantly increase the uniqueness of each piece,
bringing down the execution time.

\subsection{Run to Run Variation}

\subsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of results. However, the accuracy
of two real-world puzzles (4x4 and 8x8) has been manually confirmed,
with both achieving a 100\% correctness.

\subsection{Analysis}

It is fair to point out that the performances of the algorithm are not amazing,
but they are good enough to achieve the objectives of this paper \cref{document:objective}.
It is also worth remembering that the problem itself is extremely complex.
Using the formula introduced in section \cref{document:proof_definitions} we can calculate that a 64 piece puzzle,
like the one that has been solved before, has approximately \(4 \cdot 10^{127}\) possible combinations.
\[C = N! \cdot 4^N =  64! \cdot 4^{64} \approx 4.32 \cdot 10^{127}\]

>>>>

\subsubsection{The Levels}

@@

\subsubsection{The Behaviors}

@@

\subsubsection{Combining four objects}\label{document:combining_four_objects}
When combining four objects into one, some comparisons are executed to
ensure that the resulting piece is a valid  combination.

\begin{itemize}
  \item The right side of the object in the top left position is compared with the left side of the object in the top right position~\cref{fig:merge_pieces}(1).
  \item The bottom side of the objection the top right position is compared with the top side of the object in the bottom right position~\cref{fig:merge_pieces}(2).
  \item The left side of the objection the bottom right position is compared with the right side of the object in the bottom left position~\cref{fig:merge_pieces}(3).
  \item The top side of the objection the bottom left position is compared with the bottom side of the object in the top left position~\cref{fig:merge_pieces}(4).
\end{itemize}

@@

This section measures the execution time of many puzzles,
and plots the results. The puzzles that has been used for
this test has been described in ~\cref{document:dataset}.

The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in
section~\cref{document:combining_four_objects} were set at different values
depending on the nature of the puzzle (real or digital).

\subsubsection{Effect of Jitter on Execution Time}

As mention in \cref{document:dataset} the digital puzzle have an attribute called jitter.
Intuitively increasing the jitter would make the pieces harder to
match with each other, and consequently making the puzzle easier to solve.
And we can observe that this intuition is correct in the table below.

\begin{figure}[h]
  \caption{Effect of jitter on jigsaw pieces}\label{fig:jiiter}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/jitter.png}
\end{figure}

This shows how the execution time can be six times faster just by making
each piece more unique.
\subsection{Run to Run Variation}

\subsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of results. However, the accuracy
of two real-world puzzles (4x4 and 8x8) and one digital puzzle (16x16) has been manually confirmed,
with them achieving a 100\% correctness.

\subsection{Answering The Question}

@@
